\en{
\section{Installation}
To work with this project, clone the repository. It is recommended to do this manually and not with a tool like Android Studio, as the root of the gradle project is not the very first folder, but instead the android-app folder contained in it.

To now work with the project, open the android-app folder as a new project in Android Studio. Android Studio should now automatically guide you through the rest of the setup and install all dependencies.
}

\de{
\section{Installation}
Um an diesem Projekt zu arbeiten, klone das Git Repository. Dies sollte manuell geschehen, und nicht via Android Studio, da der root Ordner des gradle Projekts nicht der oberste Ordner ist, sondern der enthaltene android-app Ordner.

Um an dem Projekt zu arbeiten, öffne den android-app Ordner al ein neues Projekt in Android Studio. Android Studio sollte dich jetzt durch die weitere Einrichtung führen und alle Abhängigkeiten automatisch installieren.
}

\en{
\subsection{Installing Fastlane}
To use fastlane, you first need to install Ruby, and then fastlane. To install fastlane, \href{https://docs.fastlane.tools/\#installing-fastlane}{follow these instructions}. More information on fastlane can \href{https://fastlane.tools}{be found here}.
}

\de{
\subsection{Fastlane Installieren}
Um Fastlane nutzen zu können, muss zuerst Ruby, und dann Fastlane installiert werden. Um Fastlane zu installieren, \href{https://docs.fastlane.tools/\#installing-fastlane}{folge diesen Anweisungen}. Mehr Informationen zu Fastlane können \href{https://fastlane.tools}{hier} gefunden werden.
}

\label{sec:installFastlane}